% File: user_manual.tex
% Description: TeX file to generate User Manual (template)
% Author: George Hadley
% Website: http://nbitwonder.com
% Notes:
% 1) This document is written using the LaTeX typesetting language. For a beginner's
%	guide to the LaTeX typesetting language, consult http://en.wikibooks.org/wiki/LaTeX
% 2) This document needs to be compiled using pdfLaTeX. It is not compatible with pdfTeX 
%	at the present time.
% 3) This document utilizes the nbwheader function, located in the doc_header.tex file.
%	This file is located at /path-to-documentation-templates/lbr/doc_header.tex.
% Version: 0.2
% Last Modified: 1-04-2010

\documentclass[12pt,letterpaper,onecolumn]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfig}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{kpfonts}
\usepackage{fullpage}
\usepackage{hyperref}

%Pathway to global documentation library functions
%Modify to /path-to-documentation-templates/lbr
\newcommand{\globallbr}{../lbr}

%Page layout settings
\setlength{\marginparsep}{0pt}
%\setlength{\hoffset}{-0.75cm}
\setlength{\textwidth}{450pt}
\setlength{\marginparwidth}{0pt}
\begin{comment}
  Hyperref settings: settings for the hyperref hyperlink package.
  For a more detailed listing of available settings, consult 
  	http://en.wikibooks.org/wiki/LaTeX/Hyperlinks#Customization

  IMPORTANT: For your document, modify the pdftitle, pdfauthor, pdfsubject,
	and pdfkeywords options to tailor to your document
\end{comment}
\hypersetup{
	bookmarks=true, 					%Enable pdf bookmarks
	pdfborder={0,0,0},					%Disable borders around links
	pdftitle={User Manual (template)},			%Name of PDF document
	pdfauthor={George Hadley},				%Author of PDF document
	pdfsubject={Embedded Electronics},		%Subject of PDF document
	pdfkeywords={diy,electronics,nbitwonder},	%Keywords for PDF document
	colorlinks={true},					%Enable colored links
	linkcolor=red,						%Internal link color
	citecolor=green,						%Citation link color
	filecolor=blue,						%File link color
	urlcolor=blue						%URL link color
}

\input{\globallbr/doc_header.tex}
\input{\globallbr/aliases.tex}

\begin{document}
%Include header or title page here
\nbwheader{User Manual}{ProjectName}{ProjectVersion}

%Include table of contents here
\tableofcontents
\newpage
\begin{comment}
Section: Introduction
Description: Briefly describe the product, it's purpose, it's function. Describe the items that should
	have come with the product (all boards, SD card, batteries, etc.). Describe any complementary
	items that can be used with the product (accessories, etc.)
\end{comment}
\section{Introduction}

\begin{comment}
Section: Usage Instructions
Description: Information related to the usage of the project. Describe any assembly information
	needed for this project (if the project doesn't come fully assembled). Detail navigation through
	any and all software menus. Describe important basic procedures, such as changing the batteries
	or replacing the SD card.
\end{comment}
\section[Usage]{Usage Information}

\begin{comment}
Section: Safety Information
Description: Their may be some relevant safety issues for your project that users should know. Some
	are very trivial (choking hazard, keep away from water). Some may be special information relevant
	to your product (example: if your product contains a laser, a warning about not pointing it in a
	person's eyes is probably reasonable)
\end{comment}
\section[Safety]{Safety Information}

\begin{comment}
Section: Care Information
Description: Information about maintaining a product. This section might contain information about
	replacing the batteries, or conditions for storage (ex. store in a cool, dry place). Additionally, any
	disposal or recycling instructions should be included here.
\end{comment}
\section[Care]{Care Information}

\begin{comment}
Section: Support Information
Description: Technical support and other relevant information. This section might include frequently
	asked questions or common troubleshooting steps. Also, add any contact information (email,
	website, phone) for additional support information for your product.
\end{comment}
\section[Support]{Support Information}

\begin{comment}
Section: Legal Information
Description: Some types of products and equipment may have important legal considerations related
	to their use (example: for recording equipment, recording private conversations as a third-party
	is illegal in many states). Provide the user with any important legal information to help keep them,
	and your company, safe from lawsuits. Additionally, consider adding licensing information (even if
	you're using an open license) in this section. If your product is to have a warranty, this section is
	where you'll want to include that.
\end{comment}
\section[Legal]{Legal Information}

\end{document}
